Hot and fresh: evidence of climate-related suboptimal conditions for seagrass in a large Gulf coast estuary

### 2024-02-02 manu-draft.qmd
slight word edit

Long-term meteorological data showed increasing trends for air temperature and precipitation ([@fig-meteowqraw]). Mean annual air temperature has increased by `r airtempslo` $^\circ$C per year (`r airtemppvl`, $R^2$ `r airtemprsq`). Mean annual air temperature in 1975 was `r airtempstr` $^\circ$C, whereas current mean annual air temperature in 2022 was `r airtempend` $^\circ$C, showing an overall increase in the period of record of `r airtempdif` $^\circ$C. Similarly, total precipitation during the rainy season has increased by `r prpslo` mm per year, although the model was not significant (`r prppvl`). Removing September from the rainy season showed a significantly increasing trend of `r prpslo2` mm per year (`r prppvl2`, $R^2$ = `r prprsq2`; September alone did not have a significant trend, `r seppvl`). Using this model, total precipitation in 1975 was `r prpstr2` mm, whereas current total precipitation in 2022 was `r prpend2` mm, showing an overall increase in the period of record of `r prpdif2` mm. Notably, trends for the dry season (October through May) were not significant (`r drypvl`), except April which had a significantly increasing trend (`r aprpvl`, $R^2$ = `r aprrsq`). The SPI showed notable anomalies in precipitation, with pronounced rainy periods in the early 1980s, late 1990s, 2005, and 2015-2020.

>>>>

Long-term meteorological data showed increasing trends for air temperature and precipitation ([@fig-meteowqraw]). Mean annual air temperature has increased by `r airtempslo` $^\circ$C per year (`r airtemppvl`, $R^2$ `r airtemprsq`). Mean annual air temperature in 1975 was `r airtempstr` $^\circ$C, whereas current mean annual air temperature in 2022 was `r airtempend` $^\circ$C, showing an overall increase in the period of record of `r airtempdif` $^\circ$C. Similarly, total precipitation during the rainy season has increased by `r prpslo` mm per year, although the model was not significant (`r prppvl`). Removing September from the rainy season showed a significantly increasing trend of `r prpslo2` mm per year (`r prppvl2`, $R^2$ = `r prprsq2`; September alone did not have a significant trend, `r seppvl`). Using this model, mean precipitation in 1975 was `r prpstr2` mm, whereas current mean precipitation in 2022 was `r prpend2` mm, showing an overall increase in the period of record of `r prpdif2` mm. Notably, trends for the dry season (October through May) were not significant (`r drypvl`), except April which had a significantly increasing trend (`r aprpvl`, $R^2$ = `r aprrsq`). The SPI showed notable anomalies in precipitation, with pronounced rainy periods in the early 1980s, late 1990s, 2005, and 2015-2020.
